A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw

This future work holds many challenges which once again will go in two
different directions: gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogeneous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15}. Diversity, as in any other
evolutionary algorithm, seems to be the key, but there are many ways of
approaching it.

>>>>

We have also proved in this paper, through an experiment with a
massive number of users, that in fact the single factor predicting the
time needed to reach the solution is the compression entropy, meaning
that it is not so much the raw number of users, but the fact that they
contribute fit individuals to the pool in such a way that it increases
its diversity early in the experiment; that is, it is much better a
few users with different types of computers and browsers contributing
at the same time that more users with exactly the same computer and
browser contributing more or less synchronously. This also implies
that it is obviously better to manage as many users as possible to
contribute at the same time and at the beginning of the experiment,
which might not really be possible; however, the reboot strategy used
in the latest versions really contributed to this early boost in
diversity. It is interesting also to note that this boost in
performance due to client contribution diversity is due to the fact
that we are running an evolutionary algorithm, where diversity is an
essential component.

These last result has also got implications for architecture
design. For instance, it might be interesting to combine clients in
the browser with other kind of clients that contribute mainly to
diversity. In fact, early experiments with other type and more
difficult problem point in this direction. Besides, user-interaction
strategies attracting users to experiment instances at the very
beginning, like announcing it in social media, might help too to
achieve higher performance.

This is one of the changes we intend to explore in the future, which
holds many challenges, such as gathering more users and improving the
efficiency of the algorithm run in an asynchronous way by the
users. In the first case, it will be interesting to make it more {\em
  social} by comparing local performance to other's contributions, and
showing it in a graph or being able to tweet advances or the fact that
the solution has been found. Anything that keeps the users running the
system and attracts new users will contribute to the speed of finding
the solution. And the algorithm will have to be improved, mainly by
making the population more diverse. Right now there is a rigid policy
of contribution to the pool: send the best individual, but this could
be relaxed. Some other policies could also be tested, as well as
running heterogeneous algorithms in the same way that was done in
\cite{DBLP:journals/grid/ValdezTGVO15anonymous}. Diversity, as in any other
evolutionary algorithm, seems to be the key, but there are many ways of
approaching it.
